Wikipedia Text Mining and Entropy Analysis

### 2019-03-04 wiki_entropy/wiki_clustering.Rmd
issues with apply and dim(X) in MIMCA for non-word order WALS imputation

wa <- fair_wf %>% 
  filter(language %in% LANGUAGES) %>%
  select(`1A`:`19A`, language) %>%
  group_by(language) %>%
  slice(1) %>%
  gather(feature, value, `1A`:`19A`) %>%
  group_by(feature) %>%
  mutate(value = factor(value)) %>%
  ungroup() %>% 
  spread(feature, value) %>% 
  column_to_rownames("language") %>%
  as.data.frame(stringsAsFactors = TRUE) %>%
  clean_names() %>% 
  lapply(factor) %>%
  lapply(as.numeric) %>%
  lapply(factor) %>%
  as.data.frame() %>% 
  MIMCA(ncp = 4, maxiter = 100000, threshold = 1e-1)

@@

@@

wo_wf <- wf %>% 
  filter(language %in% LANGUAGES) %>%
  select(-wals.code, -latitude, -longitude, -glottocode, -`84A`)

>>>>

wa <- fair_wf %>% 
  filter(language %in% LANGUAGES) %>%
  select(`1A`:`19A`, language) %>%
  group_by(language) %>%
  slice(1) %>%
  gather(feature, value, `1A`:`19A`) %>%
  group_by(feature) %>%
  mutate(value = factor(value)) %>%
  ungroup() %>% 
  spread(feature, value) %>% 
  column_to_rownames("language") %>%
  sapply(as.factor) %>%
  as_data_frame() %>%
  MIMCA(ncp = 1, maxiter = 100000, threshold = 1e-1)

@@

wo_wf <- wf %>% 
  filter(language %in% LANGUAGES) %>%
  select(language, `82A`:`97A`) %>%
  select(-`84A`)

@@
